---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis-CI Build Status](https://travis-ci.org/jacobkap/meditations.svg?branch=master)](https://travis-ci.org/jacobkap/meditations)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jacobkap/meditations?branch=master&svg=true)](https://ci.appveyor.com/project/jacobkap/meditations)
[![Coverage status](https://codecov.io/gh/jacobkap/meditations/branch/master/graph/badge.svg)](https://codecov.io/github/jacobkap/meditations?branch=master)


# Overview

View the wisdom of Marcus Aurelius through his quotes from his book Meditations.

## Installation

You can install meditations from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jacobkap/meditations")
```

## Example

This is how to use this simple package. `meditations()` will print a random quote from the book. 

```{r example}
meditations::meditations()
```

Choose a number between 1 and 507 (there are only 507 quotes) and it will print that specific quote(s).

```{r}
meditations::meditations(5)
```


You can get the vector of all 507 quotes by

```{r}
data("meditations_quotes")
```

